\documentclass[10pt]{article}

\RequirePackage{color,graphicx}
\usepackage{newcent,multicol,multirow,tabularx,xunicode,xltxtra,url,parskip}
\usepackage[absolute]{textpos}
\usepackage[compact]{titlesec}
\usepackage[left=1.0in, right=1.0in, top=0.7in, bottom=0.7in]{geometry}
\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\usepackage[xetex,
  unicode,
  pdfencoding=auto,
  pdfinfo={
    Title={tjmaynes/cv},
    Author={TJ Maynes},
    Subject={TJ Maynes CV},
    Keywords={javascript, golang, python, generalist, agile developer},
    Producer={xelatex},
    Creator{xelatex}}]{hyperref}
\defaultfontfeatures{Scale=MatchLowercase,Mapping=tex-text}
\defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}

\def\labelitemi{--}

\begin{document}
\pagestyle{empty}

\moveleft.5\hoffset\centerline{\huge TJ Maynes}

\vspace{0.1in}
\begin{multicols}{2}
  \setlength{\parskip}{0pt}
  \begin{tabularx}{\linewidth}{@{}l X@{}}
    \textsc{location}    &\small{New York, New York}\\
    \textsc{phone}       &\small{803-526-6674}\\
    \textsc{email}       &\href{mailto:tjmaynes@gmail.com}{tjmaynes@gmail.com}\\
  \end{tabularx}

  \columnbreak

  \begin{tabularx}{\linewidth}{@{}l X@{}}
    \textsc{website}     &\href{https://www.tjmaynes.com}{tjmaynes.com}\\
    \textsc{github}      &\href{https://www.github.com/tjmaynes}{github.com/tjmaynes}\\
    \textsc{linkedin}    &\href{https://www.linkedin.com/in/tjmaynes}{linkedin.com/in/tjmaynes}\\
  \end{tabularx}
\end{multicols}

\section*{Professional Experience}
{\sl \textbf{NBCUniversal Media, LLC}} \hfill December 2016 - Present \\
Software Engineer II \hfill New York, NY
\begin{itemize}
  \item Pair programmed and test-drove a Clojure-based microservice that automated the manual input of metadata across thousands of programs which resulted in saving our business unit millions of dollars. The service was deployed on AWS ECS and used AWS RDS and Elasticsearch services.
  \item Test-drove a ReactJS-based website to enable Spanish and English-speaking World Cup viewers to watch authenticated World Cup games on Telemundo which resulted in millions of these users being informed with ways to watch the final series of World Cup games. The website was built using server-side rendering via an ExpressJS backend and deployed on AWS ECS.
  \item Pair programmed and test-drove an Elixir-based Backend-for-Frontend (BFF) service for our iOS team which resulted in more feature development, faster release cycles and a simpler iOS architecture. The service was deployed on AWS ECS and used AWS RDS and API Gateway.
  \item Other backend services that we implemented and managed used microservices patterns and Continuous Deployment practices, including setting up automated tests and pipelines for deploying our microservices to AWS ECS using custom tools built in-house.
\end{itemize}

{\sl \textbf{Rejuvenan Global Health, Inc}} \hfill May 2015 - December 2016 \\
Software Engineer \hfill New York, NY
\begin{itemize}
  \item Responsible for building the Rejuvenan iOS application, writing automation scripts, and contributing code to our company website and backend services. Setup a continuous integration pipeline using Travis-CI and Fastlane for our iOS projects, jobs included kicking off unit tests and new build artifacts from master.
  \item Added new features to a growing Ruby-on-Rails backend, which included unit and integration tests. Maintained older backend services written in Java (Spring Framework), including adding a feature to push logs to an AWS S3 bucket and writing unit tests.
\end{itemize}

{\sl \textbf{Spatial Networks Inc.}} \hfill February 2013 - August 2013 \\
Internship/Part-Time \hfill Clearwater, FL
\begin{itemize}
  \item Assisted in the development of a geographical data collection web application.
  \item Debugged and fixed front-end UI/UX issues.
  \item Started development on an Admin dashboard using Coffeescript and D3js.
Assisted in the design and development of a geographical data collection application. Operations included debugging/fixing frontend issues and creating an admin dashboard using Coffeescript and D3js.
\end{itemize}

\section*{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
  \textbf{Languages} &\small{Javascript, Go, Python} \\
  \textbf{Practices} &\small{Agile methodology, pair programming, test-driven development, consulting, continuous integration and delivery, continuous learning, monitoring, automated testing including unit/integration, performance and consumer-driven contract testing.} \\
  \textbf{Patterns} &\small{Clean architecture, dependency injection, strangler, functional programming, composition over inheritence, SOLID, and railway-oriented programming with Either and Maybe monads.} \\
  \textbf{Technologies} &\small{Kubernetes, NodeJS, React, SQL/MongoDB, StatsD, Docker, Make, Shell scripts, Jest/Mocha/Chai, OAuth2, Gatling tests, Cookiecutter templates, Elasticsearch/Kibana, Prometheus/Grafana, AWS Cloudformation/ECS/RDS/S3/API Gateway, Azure App Services/DevOps Pipelines/CosmosDB.} \\ 
\end{tabularx}
 
\section*{Education}
{\sl \textbf{Bachelor of Science, Computer Science}} \hfill May 2015\\
University of South Florida \hfill Tampa, FL \\
\begin{tabularx}{\linewidth}{@{}l X@{}}
  \textsc{Completed Courses} &\small{Analysis of Algorithms, Data Structures, Object-Oriented Programming, Software Testing, Operating Systems, Advanced Discrete Structures, Web Apps Design}\\
\end{tabularx}

{\sl CannyBot} \\ Team Member \hfill February 2015 - May 2015
\begin{itemize}
\item Programming the NAO Robot to draw shapes that it ``sees'' using the Python programming language and OpenCV. Concepts such as edge detection, pixel position interpolation, and forward kinematics were implemented in this project.
\end{itemize}
{\sl Senior Project}  \\ Team Leader \hfill August 2014 - May 2015
\begin{itemize}
\item Developed and delivered a video streaming application using C++, OpenCV, and OpenGL. Worked with a small team of students, managed communications between customer and team members, and built a Gantt Chart for keeping up with project tasks/milestones.
\end{itemize}

\section*{Production Experience}
{\sl \textbf{\href{http://http://www.imdb.com/title/tt2751310}{Sex Ed}}} \hfill July - August 2013 \\
Digital Image Technician \hfill Tampa, FL
\begin{itemize}
\item
Responsible for the coordination of the internal workings of the digital camera, archive and manage the digital data, create compressed dailies from raw footage and prepare all digital images for post-production.
\end{itemize}

{\sl \textbf{\href{http://www.imdb.com/title/tt1236254}{Wind Walkers}}} \hfill November - December 2013 \\
Grip/Art Department \hfill Tampa, FL
\begin{itemize}
\item
Responsible for building and maintaining all the equipment that supports cameras. This equipment, which includes tripods, dollies, tracks, jibs, cranes, and static rigs, is constructed of delicate yet heavy duty parts requiring a high level of experience to operate and move.
\end{itemize}

{\sl \textbf{\href{http://www.imdb.com/title/tt2339064}{Chu and Blossom}}} \hfill July - August 2012 \\
Grip/Electric \hfill Tampa, FL
\begin{itemize}
\item
Responsible for building and maintaining all the equipment that supports cameras. This equipment, which includes tripods, dollies, tracks, jibs, cranes, and static rigs, is constructed of delicate yet heavy duty parts requiring a high level of experience to operate and move.
\end{itemize}

{\sl \textbf{\href{http://www.imdb.com/title/tt3268422}{Edge of the Woods}}} \hfill March 2012 \\
Production Assistant \hfill Tampa, FL
\begin{itemize}
\item
Set PAs work on the physical set of the production, whether on location or on a sound stage. Duties include echoing (calling out) ``rolls`` and ``cuts'', locking up (making sure nothing interferes with a take), wrangling talent (actors) and background, facilitating communication between departments, distributing paperwork and radios, and related tasks as mandated by the ADs.
\end{itemize}

\section*{Organizations}
{\sl \textbf{Association of Texas Photography Instructors}} \hfill February 2011 - Present \\
Volunteer \hfill Arlington, TX
\begin{itemize}
\item
Worked alongside teachers and members of various high-school journalism organizations to help educate and promote photojournalism. Also, helped organize events and provide assistance where needed.
\end{itemize}

{\sl \textbf{Southern Interscholastic Press Association}} \hfill  March 2008 - March 2012 \\
Volunteer \hfill Columbia, SC
\begin{itemize}
\item
Worked alongside teachers and members of various high-school journalism organizations to help educate and promote photojournalism. Also, helped organize events and provide assistance where needed.
\end{itemize}

\end{document}
