\documentclass[10pt]{article}
\RequirePackage{color,graphicx}
\usepackage{newcent,multicol,tabularx,xltxtra,url,parskip}
\usepackage[absolute]{textpos}
\usepackage[compact]{titlesec}
\usepackage[left=1.0in, right=1.0in, top=0.7in, bottom=0.7in]{geometry}
\usepackage{titlesec}
\usepackage[
  xetex,
  unicode,
  pdfencoding=auto,
  pdfinfo={
    Title={tjmaynes/resumes},
    Author={TJ Maynes},
    Subject={TJ Maynes Resume}
}]{hyperref}
\defaultfontfeatures{Scale=MatchLowercase,Mapping=tex-text}
\defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}

\setcounter{secnumdepth}{0}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\pagestyle{empty}
\nofiles

\begin{document}

\moveleft.5\hoffset\centerline{\huge TJ Maynes}

\vspace{0.1in}
\begin{multicols}{2}
  \setlength{\parskip}{0pt}
  \begin{tabularx}{\linewidth}{@{}l X@{}}
    \textsc{location}    &\small{New York, New York}\\
    \textsc{phone}       &\small{803-526-6674}\\
    \textsc{email}       &\href{mailto:tjmaynes@gmail.com}{tjmaynes@gmail.com}\\
  \end{tabularx}

  \columnbreak

  \begin{tabularx}{\linewidth}{@{}l X@{}}
    \textsc{website}     &\href{https://tjmaynes.com}{tjmaynes.com}\\
    \textsc{github}      &\href{https://www.github.com/tjmaynes}{github.com/tjmaynes}\\
    \textsc{linkedin}    &\href{https://www.linkedin.com/in/tjmaynes}{linkedin.com/in/tjmaynes}\\
  \end{tabularx}
\end{multicols}

\begin{section}{Objective}
  Software Engineer seeking an opportunity to build scalable technology solutions within a cross functional agile team. Interests include distributed systems, consulting, test-driven development, pair programming, microservices, backend engineering, agile software development and coffee.
\end{section}

\begin{section}{Skills}
  \begin{tabularx}{\linewidth}{@{}l X@{}}
    \textbf{Languages} &\small{Javascript, Go, Python} \\
    \textbf{Practices} &\small{Agile methodology, pair programming, test-driven development, consulting, continuous integration and delivery, continuous learning, monitoring, automated testing including unit/integration, performance and consumer-driven contract testing.} \\
    \textbf{Patterns} &\small{Clean architecture, dependency injection, strangler, functional programming, composition over inheritence, SOLID, and railway-oriented programming with Either and Maybe monads.} \\
    \textbf{Technologies} &\small{Kubernetes, NodeJS, React, SQL/MongoDB, StatsD, Docker, Make, Shell scripts, Jest/Mocha/Chai, OAuth2, Gatling tests, Cookiecutter templates, Elasticsearch/Kibana, Prometheus/Grafana, AWS Cloudformation/ECS/RDS/S3/API Gateway.}
  \end{tabularx}
\end{section}

\begin{section}{Experience}
  {\sl \textbf{NBCUniversal Media, LLC}} \hfill December 2016 - Present \\
  Software Engineer II \hfill New York, NY
  \begin{itemize}
  \item Pair programmed and test-drove a Clojure-based microservice that automated the manual input of metadata across thousands of programs which resulted in saving our business unit millions of dollars. The service was deployed on AWS ECS and used AWS RDS and Elasticsearch services.
  \item Test-drove a ReactJS-based website to enable Spanish and English-speaking World Cup viewers to watch authenticated World Cup games on Telemundo which resulted in millions of these users being informed with ways to watch the final series of World Cup games. The website was built using server-side rendering via an ExpressJS backend and deployed on AWS ECS.
  \item Pair programmed and test-drove an Elixir-based Backend-for-Frontend (BFF) service for our iOS team which resulted in more feature development, faster release cycles and a simpler iOS architecture. The service was deployed on AWS ECS and used AWS RDS and API Gateway.
  \item Other backend services that we implemented and managed used microservices patterns and Continuous Deployment practices, including setting up automated tests and pipelines for deploying our microservices to AWS ECS using custom tools built in-house.
  \end{itemize}

  {\sl \textbf{Rejuvenan Global Health, Inc}} \hfill May 2015 - December 2016 \\
  Software Engineer \hfill New York, NY
  \begin{itemize}
  \item Responsible for building the Rejuvenan iOS application, writing automation scripts, and contributing code to our company website and backend services. Setup a continuous integration pipeline using Travis-CI and Fastlane for our iOS projects, jobs included kicking off unit tests and new build artifacts from master.
  \item Added new features to a growing Ruby-on-Rails backend, which included unit and integration tests. Maintained older backend services written in Java (Spring Framework), including adding a feature to push logs to an AWS S3 bucket and writing unit tests.
  \end{itemize}
\end{section}

\begin{section}{Education}
  {\sl \textbf{Bachelor of Science, Computer Science}} \hfill May 2015  \\
  University of South Florida \hfill Tampa, FL \\
\end{section}

\end{document}
